# Introduction {#intro}

## Workflow Github and Rstudio
* install git
* install R and Rstudio
* creat a Github account

* 1\. item 
    * 1.1\. item
    * 1.2\. item
* 2\. item

0. Setup git, github and Rstudio
    1. check git executable path and creat rsa key, then copy it. (via Rstudio)
    2. add this rsa key as SSH key to github account (via Github)
    3. creat user globlas with git (via shell)
1. creat git repisotory / project with Rstudio
    1. new directory with git repository: `Test.Rproj` (via Rstudio)
        1. creat an R script file and commit it: `test.R` (via Rstudio)
        2. creat new github repo with readme: `test` (via Github)
        3. push and merge the local and remote repos (via R-Shell)
    
        ```bash
        git remote add origin https://github.com/kadiRgoceR/test.git

        git config remote.origin.url git@github.com:kadiRgoceR/test.git
    
        git pull -u origin master
    
        git push -u origin master
    
        ```
        4. commit, push and pull in Rstudio
        
        see for details[@harrison2015]
  
    2. existing directory
        1. open shell and code
            
        ```bash
        git init
        ```
        2. terminate R
        
        3. follow the notes from 1.1.2 to 1.1.4
    
    3. version control
        1. fork an existing repo or creat a new one and copy the repo url (via Github)
        2. new Project with version control, paste Github repo url (Rstudio)
        3. make some changes, add a new R script, commit and push the changes to Github (Rstudio)
        
2. Branching
        1. fork a repo 
        2. do 3.2
        3. tell git the upstream version
        ```bash
        `git remote add upstream https://github.com/rstudio/bookdown-demo`
        ```
        

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015]. ddd aaa
